Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-09-20 paper/main.tex
remove unused label
write short introductory notes for application chapter

% --------------------------------------------------------------------------------------------------
\subsection{Cell-Cycle}
\label{subsection:mechanical-model-cycle}

@@

%###################################################################################################
\section{Application to \textit{E.Coli.} growing on Agar}

With the previous works of extracting the positions (see section~\ref{section:data-extraction}) for
individual cell-agents and the methods to estiamte parameters of our agents (see section~\ref{section:parameter-estimation}), we are now ready to apply them to showcase their usefulness.

TODO explain what data we are using

>>>>

% --------------------------------------------------------------------------------------------------
\subsection{Cell-Cycle}

@@

%###################################################################################################
\section{Application to \textit{E.Coli.} growing on Agar}
\label{section:application}

To show the usefulness of our previously developed methods (see
section~\ref{section:parameter-estimation}), we will use them to estimate the parameters of a
sequence of microscopic images of growing \texttt{E.Coli}.
The data we use~\cite{https://doi.org/10.3203/iwf/k-129} (see
section~\ref{section:data-code-availability}) has been automatically segmented with the
omnipose~\cite{Cutler2022} algorithm which provides us with the necessary cell masks.
